The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
Added+formatted refs

Our results show that the major driving force for change in APIs is the call for increased functionality. The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add modules or new functionality to existing modules were the most common. We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes that were related to functionality. Following this line of thought, the desire for new functionality can be seen as a catalyst that allows further driving forces to occur (!!!better?). The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws. In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory". The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.

In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo (!!!FIND PAPERS TO CITE HERE). These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change, rather, they are ripple-effects of changes to functionality \cite{robbes2012developers}.

@@

Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to APIs to be infrequent. In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!! which means the law of Conservation of Organisational Stability is inappropriate for APIs). This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}. The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.

@@

We conclude that we were able to reverse engineer the change decisions to a large extent. This is clear from the results, which showed that 85\% of the changes were reverse engineered correctly. The kappa value of 0.812 further supports this. We interpret that the significance of this result suggests that reverse engineering of change decisions can be done in situations where a perfect result is not required. In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile (!!!this sentence weird - yeah). This line of thought is supported by our results, which, in summary, show that we are able to reverse engineer the most major trends with very high accuracy, but that certain nuances of the changes can be misinterpreted.

@@

\section{Acknowledgements}
We would like to thank Axis and that project at GU.

>>>>

Our results show that the major driving force for change in APIs is the call for increased functionality. The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add modules or new functionality to existing modules were the most common. We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes that were related to functionality. Following this line of thought, the desire for new functionality can be seen as a catalyst that allows new change to occur. The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws. In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory". The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.

In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo \cite{dig2005role, xing2006refactoring, henkel2005catchup, dig2006apis}. These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change, rather, they are ripple-effects of changes to functionality \cite{robbes2012developers}.

@@

Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to APIs to be infrequent. In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which is the main cause for the law of Conservation of Organisational Stability not applying to APIs. This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}. The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.

@@

We conclude that we were able to reverse engineer the change decisions to a large extent. This is clear from the results, which showed that 85\% of the changes were reverse engineered correctly. The kappa value of 0.812 further supports this. We interpret that the significance of this result suggests that reverse engineering of change decisions can be done in situations where a perfect result is not required. In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile. This line of thought is supported by our results, which, in summary, show that we are able to reverse engineer the most major trends with very high accuracy, but that certain nuances of the changes can be misinterpreted.

@@

\section{Acknowledgements}
We would like to thank company A and that project at GU.
